Wetting of the adhesive fluid controls underwater adhesion in insects

### 2021-02-15 source/tex/ladybug_adhesion.tex
modified Thomas corrections
checked British English spelling
updated figure 9 reference number

\title{Wetting properties of the adhesive fluid allows beetles to attach to surfaces not just in air but also underwater}

@@

\phone{+49 6131 379 111}

\fax{+49 6131 379 310}

@@

Many beetles can climb smooth surfaces using hairy adhesive pads on their legs. It was previously shown that a terrestrial beetle can even adhere and walk underwater. The naturally hydrophobic hairs trap an air bubble around the pads, allowing the hairs to make contact to the substrate like in air. However, it remained unclear to what extend such an air bubble is necessary for underwater adhesion and if the bubble contributes to the net adhesive force. To investigate the role of the bubble, we measured the adhesive forces in individual legs of live but constrained ladybug beetles underwater in the presence and absence of a trapped bubble and compared it with its adhesion in air. Our experiments revealed that on a hydrophobic substrate, even without a bubble, the pads show adhesion comparable to that in air. On a hydrophilic substrate, underwater adhesion is significantly reduced, with or without a trapped bubble. We modelled the adhesion of a hairy pad using capillary forces. Coherent with our experiments, the model demonstrates that the wetting properties of the adhesive fluid alone can determine the insects' adhesion in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion. 
\end{abstract}

@@

The question on how insects and other small arboreal animals climb smooth and slippery
surfaces has fascinated scientists for the past three centuries \cite{RN198,RN59}. We now know that such animals are able to adhere by using specialised organs on their feet called adhesive pads. These adhesive pads can generally be described as either ``smooth'' or ``hairy''. Several insect orders including earwigs, flies, and beetles \cite{Gorb:2001b} but also several spiders \cite{Coddington:1991} and arboreal lizards \cite{Williams:1982} bear hairy pads. Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20}, which makes them suitable to adhere to most surfaces reversibly. The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) like seen in spiders and lizards but are typically undivided in most insects. The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\cite{RN19}. Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\cite{RN79}, illustrating the role of hair geometry in adhesion. All insect pads secrete an adhesive fluid while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion''). In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored. Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} using suction cups to adhere to surfaces. However, underwater adhesion using secreted liquids (glue-like substances or the adhesive fluid) requires the displacement of the water in the interface first and a spreading of the fluid on the substrate. Furthermore, the spreading coefficient of the secreted liquid needs to be larger than that of the water in order to utilise the interfacial tension between the liquids as an adhesive force. One relative simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}. This has been shown in a recent study by \citet{RN87} on the ability of a terrestrial leaf beetle which can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic hairs trap the bubble around the pads when being submerged, which de-wets the surface effectively on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the dewetted area results in its adhesion underwater. However, it remained unclear whether an air bubble is strictly necessary and its exact contribution to the adhesive force. The oily adhesive fluid found in insects alone might be sufficient in creating the necessary interfacial tension even without an bubble, given that the adhesive fluid remains on the hairs when submerged. In beetles, the tip of each seta secretes approximately one femtoliter of oily adhesive fluid \cite{RN108}. The fluid's chemical composition is identified as a mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol\cite{RN221,RN222} rendering it immiscible with water. %A recent study by Gernay et. al.\cite{RN77}, based on an elastocapillary model, has been able to reasonably predict single seta adhesion forces theoretically, confirming the dominant role of surface tension in the ``wet adhesion'' of beetles.

% Geckos are also known to adhere underwater, where its shear adhesion force on hydrophobic substrates are similar in both air and underwater conditions. Interestingly, its adhesion on a fluorinated substrate is even larger underwater than in air\cite{RN15}. This has been partially explained by a thermodynamic work of adhesion model, assuming full displacement of water at the interface, leading to a dry ``van der Waals'' contact of hairs with the surface\cite{RN199}.

The goal of this paper is to provide a generalised picture of adhesion in insects which use hairy pads and secrete a oily fluid for attachment. We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion of individual adhesive pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces. We further tested whether the chemical profile of the adhesive fluid changes when the hairs being submerged in water. Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions. The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion. Finally, we
discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals.

@@

Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We characterised adhesion by the pull-off force
during detachment and tested smooth glass and
fluorinated surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the contact type
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the bubble's role in underwater adhesion. Adhesion force
for each of the labelled contact types were compared for both substrates.

@@

Seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
purchased from Katz Biotech (Baruth, Germany) and housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with daily access to sunlight. They were fed with raisins, honey and
water \emph{ad libitum}.

 %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
An individual beetle was first carefully anesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micromanipulators in all three axes before the experiments. One front left leg was carefully fixed to a piece of soft solder wire coming off the steel ball using Blue-Tac (X) allowing us to further align the leg to the substrate. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate. Each leg of a male ladybug beetle has two pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blue-Tac without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fiber optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N/m) constitutes
the (vertical) force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A plastic
3D printed substrate holder was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The sensor was mounted on a stage
consisting of a X-piezo, used for precise lateral movements, XYZ motors,
for coarse movements and a goniometer, for adjusting substrate alignment
with the optics. Additionally, a separate Z-piezo, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. A coaxial illuminated tube microscope
(\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with digital video cameras (\emph{FLIR Blackfly S}, 2448 x 2048 pixel; XBasler)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate with help of epi-illumination.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used together to perform approach-retract
adhesion tests with the substrate to get the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textgreek{m}m lateral sliding motion was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
A further 10 \textgreek{m}m compression step (approach) set all hairs in slight compression which helped further contact
with the surface. Next, a short pause (1 s) removed any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion was done
at a speed of 62.5 \textgreek{m}m/s. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder. In order to achieve an underwater contact without
a trapped air bubble, the water was first degassed in a vacuum chamber
at 10 mbar pressure for 3 hours and used immediately. Before the experiments,
the pad was brought into contact with the surface 10 times repeatedly 
to equilibrate the pad system (X what do you mean by equilibrate?).

@@

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{Figure1-Setup_schematic}
\par\end{centering}
\caption{\label{fig:Setup} Adhesion setup (for explanation see text). The recorded force data and
contact area of a distal pad are shown in the plot, in which, the shaded
regions represent distinct movements like approach, lateral pull, pre-load and detachment... (please explain which ones X). Negative force values
represent attraction and the minimum force peak during the final retraction
step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material Xshould we provide one?}
\end{figure}

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the final retraction step (Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension effects. This effect needed to be canceled. So, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force data with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

@@

Standard 20 mm wide glass coverslips were used as the hydrophilic
substrate. Glass was wiped with isopropanol, rinsed in water and dried
under nitrogen flow. The surface was then plasma cleaned in a oxygen
plasma chamber (Diener Electronic Femto) for 10 min at 120 W. The
surface was further rinsed with water and dried under nitrogen flow.

For the hydrophobic substrate, the glass cover slip was coated with
a fluorosilane via chemical vapor deposition (CVD). First, the glass
was cleaned using IPA and plasma treated as before. Next, 0.2 ml of
Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
Sigma Aldrich, was put in a sealed chamber along with the the cleaned
glass. The chamber was placed under 100 mbar pressure for 10 min for
the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
for 3 hours.

The substrate wettability was characterised by dynamic contact angle
measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
Milli-Q water and n-hexadecane were used as test liquids. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textgreek{m}l and with 0.5 \textgreek{m}l/s flow rate.

@@

A previous study on archanids \cite{RN223} reported that its secreted
fluid does not dissolve in water. To test whether the beetles retain
their adhesive fluid underwater unchanged, we performed a Field Desorption Mass Spectroscopy
(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
were done on the extracted secretions before and after rinsing its
legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
axyridis} X the fact we are introducing a new species is a bit odd and could raise a question with the reviewer but I don't know a good way around it. we could bring it in the introduction and say that these are preliminary/unpublished results. that would be perfectly viable) was immersed in 50 \textmu L THF for 20 min and then transferred
to the measurement chamber of the FDMS. As a reference, pure THF was
used. The second middle leg of the same ladybird was subsequently
immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
20 min and then transferred to the measurement chamber of the spectrometer.
Molecular composition was extracted from the peak positions of the
FDMS spectra.

@@

In air, adhesion forces of the distal pad of ladybug beetle against
glass and PFOTS were similar, i.e. no significant differences were
detected (Figure \ref{fig:Effect-of-contact} and Table \ref{tab:Statistical-analysis}).
In contrast, the underwater adhesion on a PFOTS surface was significantly
larger than on glass (p < 0.001). This stronger adhesion on PFOTS
is observed both in the presence and absence of a trapped bubble.
In both cases, adhesion force reach similar values as in air. In contrast,
on glass, adhesion underwater is significantly reduced as compared
to dry conditions, irrespective of the presence of a trapped bubble
(p $\leq$ 0.002). In the presence of a bubble, underwater adhesion on glass was slightly higher (CLES = 0.84, p = 0.07).

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing single
leg adhesion force measurements of ladybug beetle (\emph{Coccinella
septempuctata}) on glass and PFOTS substrates in air and underwater
conditions. The two types of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
represent theoretical predictions of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textgreek{m}m,
pad diameter = 200 \textgreek{m}m, hair height = 40 \textgreek{m}m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the adhesive fluid in air and water were assumed to be
24 mN/m and 48 mN/m respectively and water surface tension is 72 mN/m.}
\end{figure}

@@

FDMS results confirm the presence of adhesive fluid on an Asian ladybird's
leg when underwater (Table \ref{tab:Molecular-distribution-of}).
Molecular weights of the secreted fluid mixtures extracted from the
beetle's leg, without and after immersion in water, show that, except
for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
fingerprint remained unchanged This indicates that the adhesion fluid
was not washed away underwater. Probable compounds in the fluid, corresponding
to the resultant molecular weights, include mostly aliphatic hydrocarbons
with traces of aldehydes.

\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|}
\hline 
Without rinsing (g/mol) & After rinsing (g/mol) & Probable compounds\tabularnewline
\hline 
\hline 
324.5 & 324.5 & C\textsubscript{23}H\textsubscript{48}, C\textsubscript{22}H\textsubscript{44}O\tabularnewline
\hline 
 & 331.6 & C\textsubscript{24}H\textsubscript{44}\tabularnewline
\hline 
350.5 & 350.5 & C\textsubscript{25}H\textsubscript{50}\tabularnewline
\hline 
352.5 & 352.5 & C\textsubscript{25}H\textsubscript{52}, C\textsubscript{24}H\textsubscript{48}O\tabularnewline
\hline 
378.5 & 378.5 & C\textsubscript{27}H\textsubscript{54}\tabularnewline
\hline 
404.6 & 404.5 & C\textsubscript{29}H\textsubscript{56}\tabularnewline
\hline 
406.8 &  & C\textsubscript{29}H\textsubscript{58}\tabularnewline
\hline 
432.8 & 432.7 & C\textsubscript{31}H\textsubscript{60}\tabularnewline
\hline 
\end{tabular}\caption{Molecular weights of adhesive fluid secretion of \emph{Harmonia axyridis}
with and without rinsing the beetle's leg in water. Molecular weights
were extracted from the peaks in the FDMS spectra. \label{tab:Molecular-distribution-of}}
\end{table}

@@

(X check for the past tense where applicable X)
\begin{figure}[H]
\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}\caption{\label{fig:Model}The capillary bridge model. The hairs make contact
with the substrate in three ways: a) \emph{In air}, where the adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the adhesive fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the adhesive fluid bridges are
inside the bubble while others are outside in water. The corresponding
ventral view contact images of the beetle's pad are shown on the right.}
\end{figure}

>>>>

\title{Wetting of the adhesive fluid controls underwater adhesion in insects}

@@

@@

Many insects can climb smooth surfaces using hairy adhesive pads on their legs. It was previously shown that a terrestrial beetle can even adhere and walk underwater. The naturally hydrophobic hairs trap an air bubble around the pads, allowing the hairs to make contact to the substrate like in air. However, it remained unclear to what extent such an air bubble is necessary for underwater adhesion. To investigate the role of the bubble, we measured the adhesive forces in individual legs of live but constrained ladybug beetles underwater in the presence and absence of a trapped bubble and compared it with its adhesion in air. Our experiments revealed that on a hydrophobic substrate, even without a bubble, the pads show adhesion comparable to that in air. On a hydrophilic substrate, underwater adhesion is significantly reduced, with or without a trapped bubble. We modelled the adhesion of a hairy pad using capillary forces. Coherent with our experiments, the model demonstrates that the wetting properties of the adhesive fluid secretion alone can determine the insects' adhesion in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion. 
\end{abstract}

@@

The question on how insects and other small arboreal animals climb smooth and slippery
surfaces has fascinated scientists for the past three centuries \cite{RN198,RN59}. We now know that such animals are able to adhere by using specialised organs on their feet called adhesive pads. These adhesive pads can generally be described as either ``smooth'' or ``hairy''. Several insect orders including earwigs, flies, and beetles \cite{Gorb:2001b} but also several spiders \cite{Coddington:1991} and arboreal lizards \cite{Williams:1982} bear hairy pads. Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20}, which makes them suitable to adhere to most surfaces reversibly. The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) as seen in spiders and lizards but are typically undivided in most insects. The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\cite{RN19}. Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\cite{RN79}, illustrating the role of hair geometry in adhesion. All insect pads secrete an adhesive fluid (``wet adhesion'') while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion''). In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored. Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion using secreted liquids (glue-like substances or the adhesive fluid) requires the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that a terrestrial leaf beetle can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic hairs trap the bubble around the pads when being submerged, which de-wets the surface effectively on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remained unclear whether an air bubble is strictly necessary and its exact contribution to the adhesive force. The oily adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hairs when submerged. In beetles, the tip of each seta secretes approximately one femtoliter of adhesive fluid \cite{RN108}. The fluid's chemical composition was identified to be an oil-like mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol\cite{RN221,RN222}, rendering it immiscible with water.

The goal of this paper is to provide a generalised picture of adhesion in insects which use hairy pads and secrete an oily fluid for attachment. We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces. We further tested whether the chemical profile of the adhesive fluid changes when the hairs were submerged in water. Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions. The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion. Finally, we
discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals.

@@

Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We characterised adhesion by the pull-off force
during detachment, tested on smooth glass and
fluorinated surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the contact type
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the bubble's role in underwater adhesion. Adhesion force
for each of the labelled contact types were compared for both substrates.

@@

Seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
were purchased from Katz Biotech (Baruth, Germany) and housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with daily access to sunlight. They were fed with raisins, honey and
water \emph{ad libitum}.

 %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. One front left leg was carefully fixed to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.) allowing us to further align the leg to the substrate. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate. Each leg of a male ladybug beetle has two pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N/m) constitutes
the vertical force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A plastic
3D printed substrate holder was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The sensor was mounted on a stage
consisting of a X-piezo element, used for precise lateral movements, XYZ motors,
for coarse movements and a goniometer, for adjusting substrate alignment
with the optics. Additionally, a separate Z-piezo element, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. A coaxial illuminated tube microscope
(\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with digital video cameras (\emph{FLIR Blackfly S}, 2448 x 2048 px; \emph{Basler ace U}, 1280 x 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of epi-illumination.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used together to perform approach-retract
adhesion tests with the substrate to get the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped further contact
with the surface. Next, a short pause (1 s) removed any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion was done
at a speed of 62.5 \textmu m/s. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder. In order to achieve an underwater contact without
a trapped air bubble, the water was first degassed in a vacuum chamber
at 10 mbar pressure for 3 hours and used immediately. Before the experiments,
the pad was brought into contact with the surface 10 times repeatedly 
to equilibrate the pad's secretion system.

@@

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{Figure1-Setup_schematic}
\par\end{centering}
\caption{\label{fig:Setup} Adhesion setup (for explanation see text). The recorded force data and
contact area of a distal pad are shown in the plot, in which, the shaded
regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
represent attraction and the minimum force peak during the final retraction
step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material.}
\end{figure}

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the final retraction step (Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension effects. This effect needed to be cancelled. So, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force data with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

@@

Standard 20 mm wide glass cover-slips were used as the hydrophilic
substrate. Glass was wiped with isopropanol, rinsed in water and dried
under nitrogen flow. The surface was then plasma cleaned in a oxygen
plasma chamber (Diener Electronic Femto) for 10 min at 120 W. The
surface was further rinsed with water and dried under nitrogen flow.

For the hydrophobic substrate, the glass cover slip was coated with
a fluorosilane via chemical vapour deposition (CVD). First, the glass
was cleaned using IPA and plasma treated as before. Next, 0.2 ml of
Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
Sigma Aldrich, was put in a sealed chamber along with the the cleaned
glass. The chamber was placed under 100 mbar pressure for 10 min for
the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
for 3 hours.

The substrate wetting was characterised by dynamic contact angle
measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
Milli-Q water and n-hexadecane were used as test liquids. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textmu l and with 0.5 \textmu l/s flow rate.

@@

A previous study on arachnids \cite{RN223} reported that its secreted
fluid does not dissolve in water. To test whether the beetles retain
their adhesive fluid underwater unchanged, we performed a Field Desorption Mass Spectroscopy
(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
were done on the extracted secretions before and after rinsing its
legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
to the measurement chamber of the FDMS. As a reference, pure THF was
used. The second middle leg of the same ladybird was subsequently
immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
20 min and then transferred to the measurement chamber of the spectrometer.
Molecular composition was extracted from the peak positions of the
FDMS spectra.

@@

In air, adhesion forces of the distal pad of ladybug beetle against
glass and PFOTS were similar, i.e. no significant differences were
detected (Figure \ref{fig:Effect-of-contact} and Table \ref{tab:Statistical-analysis}).
In contrast, the underwater adhesion on a PFOTS surface was significantly
larger than on glass (p < 0.001). This stronger adhesion on PFOTS
was observed both in the presence and absence of a trapped bubble.
In both cases, the adhesion force reached similar values as in air. In contrast,
on glass, adhesion underwater was significantly reduced when compared
to dry conditions, irrespective of the presence of a trapped bubble
(p $\leq$ 0.002). In the presence of a bubble, underwater adhesion on glass was slightly higher (CLES = 0.84, p = 0.07).

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing single
leg adhesion force measurements of ladybug beetle (\emph{Coccinella
septempuctata}) on glass and PFOTS substrates in air and underwater
conditions. The two types of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
represent theoretical predictions of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair height = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the adhesive fluid in air and water were assumed to be
24 mN/m and 48 mN/m respectively and water surface tension is 72 mN/m.}
\end{figure}

@@

FDMS results confirm the presence of adhesive fluid on an Asian ladybird's
leg when underwater (Table \ref{tab:Molecular-distribution-of}).
Molecular weights of the secreted fluid mixtures extracted from the
beetle's leg, without and after immersion in water, show that, except
for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
fingerprint remained unchanged This indicates that the adhesion fluid
was not washed away underwater. Probable compounds in the fluid, corresponding
to the resultant molecular weights, include mostly aliphatic hydrocarbons
with traces of aldehydes. Our preliminary measurements on \emph{Harmonia axyridis} gives us confidence
to assert that, even for the case of \emph{Coccinella
septempuctata}, the adhesive fluid was not washed away from the hairs during the underwater experiments.

\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|}
\hline 
Without rinsing (g/mol) & After rinsing (g/mol) & Probable compounds\tabularnewline
\hline 
\hline 
324.5 & 324.5 & C\textsubscript{23}H\textsubscript{48}, C\textsubscript{22}H\textsubscript{44}O\tabularnewline
\hline 
 & 331.6 & C\textsubscript{24}H\textsubscript{44}\tabularnewline
\hline 
350.5 & 350.5 & C\textsubscript{25}H\textsubscript{50}\tabularnewline
\hline 
352.5 & 352.5 & C\textsubscript{25}H\textsubscript{52}, C\textsubscript{24}H\textsubscript{48}O\tabularnewline
\hline 
378.5 & 378.5 & C\textsubscript{27}H\textsubscript{54}\tabularnewline
\hline 
404.6 & 404.5 & C\textsubscript{29}H\textsubscript{56}\tabularnewline
\hline 
406.8 &  & C\textsubscript{29}H\textsubscript{58}\tabularnewline
\hline 
432.8 & 432.7 & C\textsubscript{31}H\textsubscript{60}\tabularnewline
\hline 
\end{tabular}\caption{Molecular weights of adhesive fluid secretion of \emph{Harmonia axyridis}
with and without rinsing the beetle's leg in water. \label{tab:Molecular-distribution-of}}
\end{table}

@@

\begin{figure}[H]
\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}\caption{\label{fig:Model}The capillary bridge model. The hairs make contact
with the substrate in three ways: a) \emph{In air}, where the adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the adhesive fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the adhesive fluid bridges are
inside the bubble while others are outside in water. The corresponding
ventral view contact images of the beetle's pad are shown on the right.}
\end{figure}

We modelled the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad were assumed
to be perfectly rigid, for simplicity. The tip of each hair has an
adhesive fluid of volume, $V_{f}$, making contact with the substrate.
The fluid is pinned to the circumference of the hair and forms a capillary
bridge of height, $d$. Similar to our experiments, we considered three
types of contacts for the pad: 1) \emph{In air}, 2) \emph{Underwater:
no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
bubble of volume, $V_{b}$, is trapped between the hairs and pinned
to the pad circumference.
